\begin{keydescription}{\texttt{ADAPTIVE\_GRID}}
This parameter specifies whether the grid is dynamically adapted. 
\begin{keytab}
   Type:    \> logical \\
   Default: \> \texttt{False}
\end{keytab}
\end{keydescription}

\begin{keydescription}{\texttt{GRID\_LAZINESS}}
This parameter specifies the tolerated percentage deviation from the
maximum segment length \texttt{MAX\_SEGLEN} for point/line insertion. The
parameter is intended to avoid repeated insertions and deletions at the same position.
Ignored if \texttt{ADAPTIVE\_GRID=False}.
\begin{keytab}
   Type:    \> real \\
   Default: \> \texttt{10.}
\end{keytab}
\end{keydescription}

\begin{keydescription}{\texttt{GRID\_REGIONS}}
This parameter specifies the x and y range of the grid to be refined. Ignored 
if \texttt{ADAPTIVE\_GRID=False}.
\begin{keytab}
   Type:    \> tuple of tuples\\
   Default: \> \texttt{(XMIN,XMAX),} if \texttt{DIMENSIONS=2} \\
            \> \texttt{(XMIN,XMAX,YMIN,YMAX),} if \texttt{DIMENSIONS=3}
\end{keytab}
\end{keydescription}

\begin{keydescription}{\texttt{MAX\_POINTS}}
This parameter specifies the maximum number of total points in the simulation. 
Ignored if \texttt{ADAPTIVE\_GRID=False}. 
\begin{keytab}
   Type:    \> integer \\
   Default: \> \texttt{10000}
\end{keytab}
\end{keydescription}

\begin{keydescription}{\texttt{MAX\_SEGLEN}}
This parameter specifies the maximum segment length. A point/line is inserted
when the/any segment length exceeds \texttt{MAX\_SEGLEN} plus a tolerance given
by \texttt{GRID\_LAZINESS}. A point/line is deleted when the/any segment length
after deletion falls below \texttt{MAX\_SEGLEN}. The units of
\texttt{MAX\_SEGLEN} are nm. Ignored if \texttt{ADAPTIVE\_GRID=False}.
\begin{keytab}
   Type:    \> real \\
   Default: \> \texttt{10.}
\end{keytab}
\end{keydescription}

\begin{keydescription}{\texttt{MIN\_DELTA}}
This parameter specifies the minimum grid spacing in x and y. Points/lines are not
inserted if (any of) the grid spacings would fall below \texttt{MIN\_DELTA}. The
units of \texttt{MIN\_DELTA} are nm. The parameter is intended to prevent the
formation of kinks in the contour due to excessive grid refinements. Ignored if
\texttt{ADAPTIVE\_GRID=False}. If only an x value is specified, the x value is copied 
and used as the y value.  
\begin{keytab}
   Type:    \> tuple (x,y) \\
   Default: \> \texttt{1.} 
\end{keytab}
\end{keydescription}

\begin{keydescription}{\texttt{TIME\_STEP}}
This parameter specifies the maximum time step in seconds. The time step may be
reduced by the program in case of numerical problems or if it would extend over
the end of a pixel dwell time.
\begin{keytab}
   Type:    \> real \\
   Default: \> required
\end{keytab}
\end{keydescription}

